Astropy - New software standards for a growing community

### 2017-09-20 main.tex
Update on Overleaf.

%% Reintroduced the \received and \accepted commands from AASTeX v5.2
%\received{July 1, 2016}
%\revised{September 27, 2016}
\draft{\today}
%% Command to document which AAS Journal the manuscript was submitted to.
%% Adds "Submitted to " the arguement.
\submitjournal{ApJ}

@@

\shorttitle{\aastex\ Astropy Project II}
\shortauthors{Astropy Project et al.}

@@

@@

Difficulty of reversing design choices
Deciding if a feature should be included
difficulty to decide where general use ends and "handy feature for some" starts, i.e. how to reject PRs or deal with maintenance burden

@@

@@

\section{Infrastructure for affiliated packages}
\subsubsection{Package template}
\subsection{Continuous integration helpers}
bsipocz should write this up
\subsection{sphinx extensions}
probably Tom R should write this up
\section{State of the Ecosystem}

@@

%\bibliographystyle{aasjournal}          
%\bibliography{bibliography}

>>>>

%% Reintroduced the \received and \accepted commands from AASTeX v5.2
%\received{July 1, 2016}
%\revised{September 27, 2016}

%% Command to document which AAS Journal the manuscript was submitted to.
%% Adds "Submitted to " the arguement.
\submitjournal{ApJ}

@@

\shorttitle{Astropy Project II}
\shortauthors{Astropy Project et al.}

@@

\draft{\today}

@@

@@

%\subsection{Difficulty of reversing design choices}
%Deciding if a feature should be included
%difficulty to decide where general use ends and "handy feature for some" starts, i.e. how to reject PRs or deal with maintenance burden

@@

\section{Infrastructure for affiliated packages}
\subsubsection{Package template}
bsipocz may write this up tif there is no other takers
\subsection{Continuous integration helpers}
bsipocz should write this up
\subsection{sphinx extensions}
probably Tom R should write this up
\section{State of the Ecosystem}

@@

\bibliographystyle{aasjournal}          
\bibliography{bibliography}
